\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-04-24 chapters/1_intro.tex
Restructure introduction

Deep convolutional neural nets (CNNs) has been successfully applied to a wide range of tasks of computer vision and pixel-level image understanding, such as \UPDATE{boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, semantic segmentation \cite{long2015fully,chen2018deeplab,kong2018recurrent}, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet}, and pose estimation \cite{wei2016convolutional,cao2017realtime}.}

\begin{itemize}
% \SOURCE{\cite{kong2018recurrent}}
\item \emph{Instance segmentation} is a task of computer vision that involves the detection of all objects in an image by performing pixel-level segmentation of each instance.   
\item Many recent successful methods for instance segmentation %, usually named \emph{proposal-based methods}, 
 use heuristic approaches that start from the classical computer vision task of \emph{object detection}, where the goal is to localize each objects using a bounding box, and then predict both a pixel-level mask of each instance and a semantic label (classify the objects in the bounding box). \TODO{Is it really general enough as a description...?} \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}
\item While effective, these approaches are \UPDATE{somewhat unsatisfying (copy/paste, change: present some faults)} because:
\begin{itemize}
\item they rely on the object detector and non-maximum suppression heuristics to count how many instances are present in the image, 
\item they tend to underperform in cluttered scenes, since instance assignment is often carried out independently for each detection; 
\item they are not usable for wiry or articulated objects (e.g. in the field of connectomics and neuron segmenation from electron microscopy images) 
\item their architecture do not usually prevent a pixel to be shared between multiple instances
\item they do not scale up well since each proposal has to be singularly processed by the CNN. 
% \item (difficult to train in an end-to-end manner: interface between instance segmentation and detection is non-differentiable)
% \item (architecture is complex and hard to tune and “debug”...?)
\end{itemize}

\item Currently there are two successful approaches used for proposal-free instance segmentation: the first ones predict associative pixel embedding vectors, where the goal is to have a CNN predicting embedding vectors that are similar only for pixels in the same instance \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; in the second type of approaches, for every pixel a set of neighboring pixels is fixed  (not necesarelly limited to the direct neighbors) and a CNN then predicts affinities, that represent how likelity it is for each of neighboring pixels to be in the same instance \cite{liu2018affinity,wolf2018mutex,xie2015holistically}

@@

\item Recent work (\cite{wolf2018mutex}, more...) shows that it is better to use \textbf{repulsion and attraction} (directly predict it with the classifier, no need to define seeds or to fix a threshold given an hierarchy of clusters)
\item solving correlation clustering problem (multicut) is too expensive for this application (even using recently proposed heuristics)
\item our contributions:
\begin{itemize}
\item we propose a unified and simple formalization of Agglomerative Clustering and show how many of the recently proposed methods can be seen as special cases (focusing in particular on signed graphs) (\textbf{review and comparison paper})
\item new clustering algorithms on signed graphs
\item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and MC energy)

\end{itemize}
\item on other datasets (connectomics) many methods are based on multi-step pipelines first predicting superpixels
\item \textit{if we get good scores on CREMI}: we show that also on neuro-data it is worth to skip the hand-crafted superpixel step and compute the final segmentation directly from the CNN affinities (MWS already showed it on the ISBI dataset)

>>>>

\begin{itemize}
\item \emph{Possible intro about aggl. clustering:} \UPDATE{Hierarchical, agglomerative clustering is an important and well-established technique in unsupervised machine learning. Agglomerative clustering schemes start from the partition of the data set into singleton nodes and merge step by step the current pair of mutually closest nodes into a new node until there is one final node left, which comprises the entire data set. Various clustering schemes share this procedure as a common definition, but differ in the way in which the measure of inter-cluster dissimilarity is updated after each step. } %\cite{mullner2011modern}

\item \emph{Other possible intro:} Many problems in computer vision involve clustering. Partitional clustering, such as k-means [1], determines all clusters at once, while agglomerative clustering [1] begins with a large number of small clusters, and iteratively selects two clusters with the largest affinity under some measures to merge, until some stopping condition is reached. Ag- glomerative clustering has been studied for more than half a century, and used in many applications [1], because it is conceptually simple and produces an informative hierar- chical structure of clusters. % FROM https://arxiv.org/pdf/1208.5092.pdf#page14

\item Get more specific about graph (we do not cluster points in a space, but we cluster vertices with specified neighbors and interactions given by edges).

\item HC is a popular graph partitioning algorithm. Why: more efficient than divisive approaches and graph cuts; does not usually require to specify the final number of clusters (e.g. spectral clustering) or seed nodes (e.g. watershed, random walker). \UPDATE{And if the graph is not dense, HC algorithms scale up well with complexity}

\item Motivation 1:

\begin{itemize}

\item all HC methods only talk about positive edge weights, but it is actually easy to generalize them for negative and attractive edges. 
\item The standard version of HC is good for building hierarchy but problem with hierarchical merge-trees is how to choose one single threshold. Choose one single fixed density level. Ideally we would like to be able to cut the tree at different places to select our clusters.
\item An important line of research is based on the observation that superior partitionings are obtained when the graph has both attractive and repulsive edges. Solutions that optimally balance attraction and repulsion do not require external stopping criteria such as predefined number of regions or seeds. This generalization leads to the NP-hard problem of correlation clustering or (synonymous) multicut (MC) partitioning. \emph{Alternative:} multicut / correlation clustering partitions vertices with both attractive and repulsive interactions encoded into the edges of a graph. Multicut has the great advantage that a “natural” partitioning of a graph can be found, without needing to specify a desired number of clusters, or a termination criterion, or one seed per region. Its great drawback is that its optimization is NP-hard.

\item Contributions: (and mention introductory Figure)
\begin{itemize}
\item We generalize the hierarchical agglomerative clustering framework to graphs with positive and negative edge attributes
\item We review both standard hierarchical clustering algorithms and signed graph partitioning algorithms by showing how they can be described in this simplified framework (and as special cases of the general algorithm presented in Sec. \ref{sec:algorithm})
\item we introduce and test new variations of these algorithms for signed graphs
\end{itemize}
\end{itemize}

\item Motivation 2:
\begin{itemize}
\item HC has been always really popular in computer vision: \emph{Instance segmentation} is a task of computer vision that involves the detection of all objects in an image by performing pixel-level segmentation of each instance.   
\item Since conventional unsigned graph agglomerative clustering algorithms, such as the well-known linkage methods [1], usually are quite sensitive to noise and outliers [1] (As their affinities are directly computed using pairwise distances between samples), most methods were based on multi-step pipelines first predicting superpixels (to reduce noise).
\item These methods are still commonly used for specific instance segmentation applications: connectomics, build merge-tree 
 %https://arxiv.org/pdf/1208.5092.pdf
\item still commonly used for building merge-trees, give recent examples in connectomics (Sebastian Seung, etc...) % https://arxiv.org/abs/1608.04051
\item Graph clustering algorithms recently gained more and more popularity with the advent of deep-learning and its application to instance segmentation
\item Deep convolutional neural nets (CNNs) has been successfully applied to a wide range of tasks of computer vision and pixel-level image understanding, such as \UPDATE{boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, semantic segmentation \cite{long2015fully,chen2018deeplab,kong2018recurrent}, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet}, and pose estimation \cite{wei2016convolutional,cao2017realtime}.}
% \SOURCE{\cite{kong2018recurrent}}

\item Currently there are two successful approaches used for proposal-free bottom-up instance segmentation: the first ones predict associative pixel embedding vectors, where the goal is to have a CNN predicting embedding vectors that are similar only for pixels in the same instance \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; in the second type of approaches, for every pixel a set of neighboring pixels is fixed  (not necesarelly limited to the direct neighbors) and a CNN then predicts affinities, that represent how likely it is for each of neighboring pixels to be in the same instance \cite{liu2018affinity,wolf2018mutex,xie2015holistically}

@@

\item GMIS achieved 
comparable results to methods based on object 
proposal like Mask-R-CNN on natural images 
(Cityscapes); MWS achieved SOA results on a 
biological images (ISBI)

\item Out contributions:

\begin{itemize}
 \item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and quality of the final clustering in terms of multicut energy) \textbf{Comparison paper}
 \item \textit{if we get good scores on CREMI dataset}: we show that also on neuro-data it is worth to skip the hand-crafted superpixel step and compute the final segmentation directly from the CNN affinities (MWS already showed it on the ISBI dataset): main selling point is again the almost-parameter free feature of the method
\end{itemize}
\end{itemize}
\end{itemize}

More details about instance segmentation (move to related work)
\begin{itemize}

\item 
\item Many recent successful methods for instance segmentation %, usually named \emph{proposal-based methods}, 
 use heuristic approaches that start from the classical computer vision task of \emph{object detection}, where the goal is to localize each objects using a bounding box, and then predict both a pixel-level mask of each instance and a semantic label (classify the objects in the bounding box). \TODO{Is it really general enough as a description...?} \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}
\item While effective, these approaches are \UPDATE{somewhat unsatisfying (copy/paste, change: present some faults)} because:
\begin{itemize}
\item they rely on the object detector and non-maximum suppression heuristics to count how many instances are present in the image, 
\item they tend to underperform in cluttered scenes, since instance assignment is often carried out independently for each detection; 
\item they are not usable for wiry or articulated objects (e.g. in the field of connectomics and neuron segmenation from electron microscopy images) 
\item their architecture do not usually prevent a pixel to be shared between multiple instances
\item they do not scale up well since each proposal has to be singularly processed by the CNN. 
% \item (difficult to train in an end-to-end manner: interface between instance segmentation and detection is non-differentiable)
% \item (architecture is complex and hard to tune and “debug”...?)
\end{itemize}

\item Currently there are two successful approaches used for proposal-free (make brief intro) instance segmentation: the first ones predict associative pixel embedding vectors, where the goal is to have a CNN predicting embedding vectors that are similar only for pixels in the same instance \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; in the second type of approaches, for every pixel a set of neighboring pixels is fixed  (not necesarelly limited to the direct neighbors) and a CNN then predicts affinities, that represent how likely it is for each of neighboring pixels to be in the same instance \cite{liu2018affinity,wolf2018mutex,xie2015holistically}

\item Recent work (\cite{wolf2018mutex}, more...) shows that it is better to use \textbf{repulsion and attraction} (directly predict it with the classifier, no need to define seeds or to fix a threshold given an hierarchy of clusters)
\item solving correlation clustering problem (multicut) is too expensive for this application (even using recently proposed heuristics)
\item our contributions:
\begin{itemize}
\item we propose a unified and simple formalization of Agglomerative Clustering and show how many of the recently proposed methods can be seen as special cases (focusing in particular on signed graphs) (\textbf{review and comparison paper})
\item new clustering algorithms on signed graphs

\end{itemize}
\item on other datasets (connectomics) many methods are based on multi-step pipelines first predicting superpixels

### 2019-04-24 chapters/2_rel_work.tex
Restructure introduction

\item \textbf{Graph clustering related work}:
\begin{itemize}
    \item popular in image segmentation: \textbf{agglomerative clustering}.
    \item Why: more efficient than divisive approaches and graph cuts; does not usually require to specify the final number of clusters (e.g. spectral clustering) or seed nodes (e.g. watershed, random walker) 
    % old graph cut paper: \cite{shi2000normalized}
    % \item \emph{[other clustering methods working in an euclidean embedding space like mean-shift, K-means, Mixture models, BIRCH... can most probably be omitted]}
    \item many segmentation pipelines used to start the agglomeration from superpixels (SLIC, \cite{felzenszwalb2004efficient}, watershed) to reduce size of the problem 
    \item usually we build an hierarchy of clusters (or a \emph{merge-tree}): \TODO{find meaningful order}
    \item clustering paper suggested by Roman

>>>>

\item \textbf{Graph clustering related work}:
\begin{itemize}
    \item popular in image segmentation: \textbf{agglomerative clustering}.
    \item {\small More from \cite{mullner2011modern}: The seven most common methods are termed single, complete, average (UPGMA), weighted (WPGMA, McQuitty), Ward, centroid (UPGMC) and median (WPGMC) linkage (see Everitt et al., 2011, Table 4.1). They are implemented in standard numerical and statistical software such as R (R Development Core Team, 2011), MATLAB (The MathWorks, Inc., 2011), Mathematica (Wolfram Research, Inc., 2010), SciPy (Jones et al., 2001).}
    \item Why: more efficient than divisive approaches and graph cuts; does not usually require to specify the final number of clusters (e.g. spectral clustering) or seed nodes (e.g. watershed, random walker) 
    % old graph cut paper: \cite{shi2000normalized}
    % \item \emph{[other clustering methods working in an euclidean embedding space like mean-shift, K-means, Mixture models, BIRCH... can most probably be omitted]}
    \item many segmentation pipelines used to start the agglomeration from superpixels (SLIC, \cite{felzenszwalb2004efficient}, watershed) to reduce size of the problem 
    \item usually we build an hierarchy of clusters (or a \emph{merge-tree}): \TODO{find meaningful order}
    \item clustering paper suggested by Roman; Cocoons

### 2019-04-24 chapters/3_algorithm.tex
Restructure introduction

\section{Unified Graph Agglomerative Clustering}
In this section we introduce the Unified Graph Agglomerative Clustering Algorithm (UGACA) that represents a simple generalized formalization of many agglomerative graph clustering algorithms. \UPDATE{It can be used to describe both unsigned clustering algorithms ingesting positive node similarities and signed clustering algorithms using attractive and repulsive cues.}\\
First, we define notation and the concept of cannot-link constraints. Then, we introduce the generalized algorithm and show \UPDATE{how it can be used to introduce several new agglomerative clustering algorithms for graphs with signed edge weights.}

@@

\begin{itemize}
\item \TODO{First define clustering, then weights, costs} We consider the problem of clustering a simple graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+$ to each edge $e \in E$ representing a merge affinity: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that several formalisms defining unsigned weighted graphs associate to each edge a positive scalar that represents a metric or distance on the graph. In these formalisms, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+: E \rightarrow \mathbb{R}^+$.}. On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates a split tendency $w_e^-$ to each edge: the higher this weight, the greater the desire of the incident vertices to be in different clusters.
Graphs that have only positive weights can be seen as special cases of the previously defined graph $\mathcal{G}(V,E,w^+,w^-)$, when $w^-_e=0$ for every $e \in E$.

\item The set $\Pi$ is defined as a partition of the set of nodes $V$ into $K$ subsets if $V = \cup_{i=1}^K S_i $ and $S_i \cap S_j = \emptyset$ for every $i\neq j \in \{1, ..., K\}$. We call a partition $\Pi$ of $V$ a \emph{clustering} if every $S \in \Pi$ induces a connected subgraph (\emph{cluster}) of $\mathcal{G}$.
\item For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^0_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^1$ the complementary set of edges whose linked nodes belong to distinct clusters:

@@

\begin{algorithm}
  \caption{Unified Graph Agglomerative Clustering \TODO{adapt to width}}
   \hspace*{\algorithmicindent} \textbf{Inputs:} graph $\mathcal{G}(V,E,W)$; bool {\color{blue}\texttt{addCannotLink}}  \\
  \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering and contracted graph $\mathcal{G}'$\\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]

@@

\subsection{The algorithm}

>>>>

\section{Unified Graph Agglomerative Clustering}
In this section we introduce the Unified Graph Agglomerative Clustering Algorithm (UGACA) that represents a simple \UPDATE{generalized} formalization of many agglomerative graph clustering algorithms. \UPDATE{It can be used to describe both unsigned clustering algorithms ingesting positive node similarities and signed clustering algorithms using attractive and repulsive cues.}\\
First, we define notation and the concept of cannot-link constraints. Then, we introduce the generalized algorithm and show \UPDATE{how it can be used to introduce several new agglomerative clustering algorithms for graphs with signed edge weights.}

@@

\begin{itemize}
\item \TODO{First define clustering, then weights, costs} We consider the problem of clustering a simple graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+$ to each edge $e \in E$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that several formalisms defining unsigned weighted graphs associate to each edge a positive scalar that represents a metric or distance on the graph. In these formalisms, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+: E \rightarrow \mathbb{R}^+$.}. On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates a split tendency $w_e^-$ to each edge: the higher this weight, the greater the desire of the incident vertices to be in different clusters.
Graphs that have only positive weights can be seen as special cases of the previously defined graph $\mathcal{G}(V,E,w^+,w^-)$, when $w^-_e=0$ for every $e \in E$.

\item We call the set $\Pi$ a \emph{partition of nodes $V$ into $K$ subsets} if $V = \cup_{i=1}^K S_i $ and $S_i \cap S_j = \emptyset$ for every $i\neq j \in \{1, ..., K\}$. A partition $\Pi$ of $V$ is a \emph{clustering} if every $S \in \Pi$ induces a connected subgraph (\emph{cluster}) of $\mathcal{G}$.
\item For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^0_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^1$ the complementary set of edges whose linked nodes belong to distinct clusters:

@@

\begin{algorithm}
  \caption{Unified Graph Agglomerative Clustering \TODO{make it one-column style}}
   \hspace*{\algorithmicindent} \textbf{Inputs:} graph $\mathcal{G}(V,E,W)$; bool {\color{blue}\texttt{addCannotLink}}  \\
  \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering and contracted graph $\mathcal{G}'$\\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]

@@

\subsection{The algorithm} \label{sec:algorithm}

### 2019-04-24 chapters/5_experiments_intro.tex
Add and update graphics
"Finish" draft of noise exp. section
Restructure introduction

\subsection{Experimental setup and tested datasets}
\begin{itemize}
    \item Define long-range grid graph. (Mention the fact of enforcing local merge)
\item Introduce "Poisson" random graph with a given probability of long-range connections
\item Comment about the short- and long-range distinction in the MWS paper? It does not work that well in practice (applying post-processing to remove small segments is easier and better solution)
\item Define offset patterns (link to supplementary material), trained networks (loss, etc...) and setups on cremi and cityscapes 
\end{itemize}

>>>>

\subsection{Experimental setup and tested datasets}
\begin{itemize}
    \item Define long-range grid graph. (Mention the fact of enforcing local merge)
\item Introduce "Poisson" random graph with a given probability of long-range connections
\item Comment about the short- and long-range distinction in the MWS paper? It does not work that well in practice (applying post-processing to remove small segments is easier and better solution).
\item Ad of course we can think about a classifier that separately predict attraction and repulsion
\item Define offset patterns (link to supplementary material), trained networks (loss, etc...) and setups on cremi and cityscapes 
\item Mention postprocessing step: get rid of tiny segments; on CREMI we use watershed to fill the deleted parts 
\end{itemize}
